Interval Probability for Fuzzy Quantum Theories

### 2016-05-18 prob.tex
prob.tex \section{Quantum Probability Spaces} updates....

\begin{definition}[Complement; Commutativity;
Independence~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between event. Given a quantum probability measure $\mu$, two projections
$P_{1}$ and $P_{2}$ are independent if $P_{1}$ and $P_{2}$ commute
and $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
\end{itemize}
\qed\end{definition}

>>>>

\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\item ~\\ \yutsung{The definition of independence is different from different
sources:\\
1. In Swart's~\cite{Swart2013}, given two $*$-algebras~$\mathscr{A}_{1}$ and
$\mathscr{A}_{2}$ which commute with each other. They are \emph{logically
independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu_{1}\otimes\mu_{2}$
on $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$ such that
$\left(\mu_{1}\otimes\mu_{2}\right)\left(A_{1}\otimes
A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$. 
Then, Swart proved the Bell inequality on logically independence $*$-algebras
with product state. The problem for us is that this defines the independent of
algebras, but not events\ldots\\
2. In Yuan's~\cite{Yuan2012}, given a $\mu$ on an $*$-algebra~$\mathscr{A}$,
two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are independent
if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
The problem for us is the same as the previous one: this defines the
independent of algebras, but not events\ldots\\
3. In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
we need first understand their notation. \cite{GuehneKleinmannCabelloEtAl2010}
focus on the hidden-variable (HV) models, but their notation may be
applied to the usual quantum model. \\
}
\end{itemize}
\qed\end{definition}
